\Huge State-Space Models and Sequential Monte Carlo methods

### 2021-07-30 final-draft.Rmd
merged
Merge branch 'main' of https://github.com/edoardo-marcelli/Progetto-Bayesian

# Conflicts:
#	prova_knit_finale.log
#	prova_knit_finale.pdf

---
header-includes:
- \usepackage{txfonts}
- \usepackage{amsmath}
- \usepackage[bindingoffset=1.5cm, left=3cm, right=3cm, top=3cm, bottom=3cm]{geometry}
- \usepackage{graphicx}
- \usepackage{MnSymbol} %allows to insert the QED at the end of the proofs
- \usepackage{hyperref} %set the hyperlink to cite sections, equations...
- \urlstyle{same}
- \usepackage{comment}
- \usepackage{enumitem}
- \usepackage{ntheorem}
- \usepackage{lipsum}
- \usepackage{amssymb}
- \usepackage{xcolor}
- \theoremstyle{break}
- \newtheorem{thm}{Theorem}% theorem counter resets every \subsection
- \renewcommand{\thethm}{\arabic{thm}}
- \newtheorem{proposition}{Proposition}
- \newtheorem{assumption}{Assumption}
- \newtheorem{lemma}{Lemma}
- \newtheorem{definition}{Definition}
- \theoremstyle{nonumberplain}
- \newtheorem{proof*}{Proof.}
- \newtheorem{definition}{Definition}
- \renewcommand{\P}{\mathbb{P}}
- \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
- \def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
- \setcounter{MaxMatrixCols}{10}
- \setlength{\oddsidemargin}{.0in}
- \setlength{\textwidth}{6 in}
- \setlength{\topmargin}{-.1in}
- \setlength{\textheight}{8.1in}
- \renewcommand{\baselinestretch}{1.5}
- \usepackage{amssymb}
- \newcommand{\E}{\mathbb E}
- \newcommand{\Q}{\mathbb Q}
- \newcommand{\M}{\mathbb M}
- \newcommand{\R}{\mathbb R}
- \newcommand{\B}{\mathcal B}
- \newcommand{\X}{\mathcal X}
- \newcommand{\Y}{\mathcal Y}
- \newcommand{\Pd}{\mathbb P}
- \newcommand{\N}{\mathcal N}
- \def\code#1{\texttt{#1}}
- \newtheorem{algorithm}{Algorithm}[section]
- \usepackage{float}
- \floatplacement{figure}{}

@@

\chapter{Markov Processes and State-Space Models}
\section{Notation}
Let us fix the basic notation that will be employed henceforth. Upper case letters, e.g. $X_t, Y_t,$ denote random variables, while lower case letters 
denote the realizations. Finite sequences are made compact using the semi-colon notation, e.g. $x_{0:t}=(x_0, x_1, \dots, x_t)$ for some $t \geq 0.$ The sets of outcomes are denoted by upper case calligraphic letters, e.g. $\mathcal{X}, \mathcal{Y}.$  The $\sigma$-algebra
of a set $\mathcal{X}$ reads $\mathcal{B}(\mathcal{X}).$ The pair $(\mathcal{X}, \mathcal{B}(\mathcal{X}))$ is a measurable space.
The densities are represented with lower case cursive letters. For example, the density of $X_t$ in $x_t$ is $p_t^\theta(x_t),$ where $\theta\in\Theta$ is some (eventually known) vector, while the density 
of $X_t$ in $x_t,$ given that $X_{t-1}$ has previously taken value $x_{t-1},$ is $p_t^\theta(x_t\mid x_{t-1}).$  Note that $p_t^\theta(x_t\mid x_{t-1})$ is a member of the parametric family with parameters $(\theta, x_{t-1})$.
The probability distribution of a random variable $X_t$ is represented by $\mathbb{P}_t(dx_t),$ while the probability distribution of a sequence $X_{0:t}$ is represented by $\mathbb{P}_t(dx_{0:t}).$ The Dirac measure, i.e., the measure that assigns probability $1$ to the singleton $\{x\},$ is denoted by $\delta_x(dy)$.The expectation operator is denoted by $\mathbb{E},$ where the section of $\mathbb{E}$ at $\mathbb{Q},$ i.e., $\mathbb{E}_{\mathbb{Q}}$ denotes the operator computed with respect to the probability distribution $\mathbb{Q}.$ 
Let $\varphi$ be a function defined on the random variable $X\thicksim\mathbb{Q}.$ Then, we denote the expected value of $\varphi(X)$ with 
$$
    \mathbb{E}_{\mathbb{Q}}[\varphi(X)]=
    \int_{\mathcal{X}}\varphi(x)\mathbb{Q}(dx).
$$
Convergence in distribution is denoted with the symbol $\implies.$ So, $X\implies\N(0,1)$ means that the random variable $X$ converges in distribution to a normal Gaussian.

>>>>

---
header-includes:
- \usepackage{txfonts}
- \usepackage{amsmath}
- \usepackage[bindingoffset=1.5cm, left=3cm, right=3cm, top=3cm, bottom=3cm]{geometry}
- \usepackage{graphicx}
- \usepackage{MnSymbol} %allows to insert the QED at the end of the proofs
- \usepackage{hyperref} %set the hyperlink to cite sections, equations...
- \urlstyle{same}
- \usepackage{comment}
- \usepackage{enumitem}
- \usepackage{ntheorem}
- \usepackage{lipsum}
- \usepackage{xcolor}
- \theoremstyle{break}
- \newtheorem{thm}{Theorem}% theorem counter resets every \subsection
- \renewcommand{\thethm}{\arabic{thm}}
- \newtheorem{proposition}{Proposition}
- \newtheorem{assumption}{Assumption}
- \newtheorem{lemma}{Lemma}
- \newtheorem{definition}{Definition}
- \theoremstyle{nonumberplain}
- \newtheorem{proof*}{Proof.}
- \renewcommand{\P}{\mathbb{P}}
- \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
- \def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
- \setcounter{MaxMatrixCols}{10}
- \setlength{\oddsidemargin}{.0in}
- \setlength{\textwidth}{6 in}
- \setlength{\topmargin}{-.1in}
- \setlength{\textheight}{8.1in}
- \renewcommand{\baselinestretch}{1.5}
- \newcommand{\E}{\mathbb E}
- \newcommand{\Q}{\mathbb Q}
- \newcommand{\M}{\mathbb M}
- \newcommand{\R}{\mathbb R}
- \newcommand{\B}{\mathcal B}
- \newcommand{\X}{\mathcal X}
- \newcommand{\Y}{\mathcal Y}
- \newcommand{\Pd}{\mathbb P}
- \newcommand{\N}{\mathcal N}
- \def\code#1{\texttt{#1}}
- \newtheorem{algorithm}{Algorithm}[section]
- \usepackage{float}
- \floatplacement{figure}{}

@@

\chapter{Markov Processes and State-Space Models}
\section{Notation}
Let us fix the basic notation that will be employed henceforth. Upper case letters, e.g. $X_t, Y_t,$ denote random variables, while lower case letters 
denote the realizations. Finite sequences are made compact using the semi-colon notation, e.g. $x_{0:t}=(x_0, x_1, \dots, x_t)$ for some $t \geq 0.$ The sets of outcomes are denoted by upper case calligraphic letters, e.g. $\mathcal{X}, \mathcal{Y}.$  The $\sigma$-algebra
of a set $\mathcal{X}$ reads $\mathcal{B}(\mathcal{X}).$ The pair $(\mathcal{X}, \mathcal{B}(\mathcal{X}))$ is a measurable space.
The densities are represented with lower case cursive letters. For example, the density of $X_t$ in $x_t$ is $p_t^\theta(x_t),$ where $\theta\in\Theta$ is some (eventually known) vector, while the density 
of $X_t$ in $x_t,$ given that $X_{t-1}$ has previously taken value $x_{t-1},$ is $p_t^\theta(x_t\mid x_{t-1}).$  Note that $p_t^\theta(x_t\mid x_{t-1})$ is a member of the parametric family with parameters $(\theta, x_{t-1})$.
The probability distribution of a random variable $X_t$ is represented by $\mathbb{P}_t(dx_t),$ while the probability distribution of a sequence $X_{0:t}$ is represented by $\mathbb{P}_t(dx_{0:t}).$ The Dirac measure, i.e., the measure that assigns probability $1$ to the singleton $\{x\},$ is denoted by $\delta_x(dy)$.The expectation operator is denoted by $\mathbb{E},$ where the section of $\mathbb{E}$ at $\mathbb{Q},$ i.e., $\mathbb{E}_{\mathbb{Q}}$ denotes the operator computed with respect to the probability distribution $\mathbb{Q}.$ 
Let $\varphi$ be a function defined on the random variable $X\propto\mathbb{Q}.$ Then, we denote the expected value of $\varphi(X)$ with 
$$
    \mathbb{E}_{\mathbb{Q}}[\varphi(X)]=
    \int_{\mathcal{X}}\varphi(x)\mathbb{Q}(dx).
$$
Convergence in distribution is denoted with the symbol $\implies.$ So, $X\implies\N(0,1)$ means that the random variable $X$ converges in distribution to a normal Gaussian.

### 2021-07-30 new-draft.Rmd
merged
Merge branch 'main' of https://github.com/edoardo-marcelli/Progetto-Bayesian

# Conflicts:
#	prova_knit_finale.log
#	prova_knit_finale.pdf

---
```{r, results= FALSE, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = '')
knitr::opts_chunk$set(out.extra='')
```
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Sys.setlocale("LC_TIME", "English")
```
```{r include=FALSE}
library(ggplot2)
library(ggpubr)
library(kableExtra)
```

>>>>

---
```{r, results= FALSE, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = '')
knitr::opts_chunk$set(out.extra='')
```
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Sys.setlocale("LC_TIME", "English")
```
```{r include=FALSE}
library(ggplot2)
library(ggpubr)
library(kableExtra)
tinytex::tlmgr_install() 
```

### 2021-07-30 nuova-final-draft.tex
merged
Merge branch 'main' of https://github.com/edoardo-marcelli/Progetto-Bayesian

# Conflicts:
#	prova_knit_finale.log
#	prova_knit_finale.pdf

  pdftitle={State-Space Models and Particle Filters},
  pdfauthor={Edoardo Marcelli; Roberto Colarieti; Alexei Verkhovtsev; Michele Bolla; Gabriele Romano; Benedetta Bruni},

@@

\title{\Huge State-Space Models and Particle Filters}
\author{Edoardo Marcelli \and Roberto Colarieti \and Alexei
Verkhovtsev \and Michele Bolla \and Gabriele Romano \and Benedetta
Bruni}
\date{21 luglio, 2021}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-5-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-7-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-10-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-13-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-16-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-19-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-22-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-25-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-26-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-32-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/unnamed-chunk-35-1}

@@

{\centering \includegraphics{backup1_files/figure-latex/cll_plot-1}

>>>>

  pdftitle={State-Space Models and Sequential Monte Carlo methods},
  pdfauthor={Edoardo Marcelli; Roberto Colarieti; Alex; Michele Bolla; Gabriele Romano; Benedetta Bruni},

@@

\title{\Huge State-Space Models and Sequential Monte Carlo methods}
\author{Edoardo Marcelli \and Roberto Colarieti \and Alex \and Michele
Bolla \and Gabriele Romano \and Benedetta Bruni}
\date{21 luglio, 2021}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-5-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-7-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-10-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-13-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-16-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-19-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-22-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-25-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-26-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-32-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/unnamed-chunk-35-1}

@@

{\centering \includegraphics{nuova-final-draft_files/figure-latex/cll_plot-1}
